%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[11pt, a4paper]{awesome-cv}

%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{cv/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-red}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Personal Data
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Essentials
\name{Richard}{Goodman}
\address{6 Hillside Way, Mouslecoomb, Brighton, BN2 4TR}
\mobile{(+44) 7 484 616 353} 
%%% Social
\email{richardagoodman@icloud.com}
\homepage{www.onegoodman.com}
\github{richardbadman}
\linkedin{richard-goodman}
%%% Optionals
\position{Bsc Computer Science with Placement Graduate}
%\quote{``Make the change that you want to see in the world."}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Letter Data (Cover Letter)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipient
  {Company Recruitment Team}
  {Jagex Ltd.\\220 Science Park\\Cambridge, CB4 0WA}
\letterdate{\today}
\vspace*{-5mm}
\lettertitle{Job Application for QA Analyst (OldSchool RuneScape)}
\letteropening{Dear Sir or Madam,}
\letterclosing{Sincerely,}
\letterenclosure[Attached]{Curriculum Vitae}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Content
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Make a footer for CV with three arguments(<left>, <center>, <right>)
\makecvfooter
  {\today}
  {Richard~~~·~~~Goodman}
  {}

\begin{document}
%%% Make a header for CV using personal data
\makecvheader

%%% Make a title for Cover Letter using letter data
\makelettertitle

%%% Write content for your cover letter
\begin{cvletter}
\cvparagraph{About Me}
I am currently finishing my studies of BSc Computer Science with Placement at the University of Brighton, where I am expected to get a first class degree. My individual project for my dissertation is creating an iOS application listing recipes where users can store dietary information on themselves as well as others \textit{(such as, vegetarian, allergic to X, Kosher etc.)}, by selecting the desired people, recipes will be filtered in order to ensure all recipes are suitable for everyone. This is being made using Swift 3.0, MySQL and the Laravel PhP framework for an API.

\cvparagraph{Why Jagex?}
Jagex's reputation is an important factor, being a multi-award winning games development company with a Guinness World Record-holding title. I would be proud to work for a company with such prestige.

From watching the videos on your website about the environment at your office, I was in awe of the comfortable and enjoyable, but hard-working balance that was in place that I believe I can be a part of. 

\cvparagraph{Why OldSchool RuneScape?}
OldSchool RuneScape just provides that nostalgia that we all love. Apart from being a fan of the game, it boasts of passion and quality to the community which I really admire. Being a passionate man for for the delivery of quality work, I consider I am suitable for the role.

Furthermore, the engagement with the community really excites me. After watching several streams of update previews as well as general discussions, I think it's such an unique aspect to not only the role, but the company that there is such a focus on listening to the community.

\cvparagraph{Why Me?}
Although being a reliable and dependable person. I feel I already have that competitive edge having gained a years experience in the IT industry from my placement. With this I have learned skills that can't be taught at university, such as working in teams to a standard that you are representing a world-leading company. As well as having responsibilities of maintaining database systems and having the opportunity to design and create new systems for the company. Using these kind of skills, I feel I can become a valuable member of the team.

\end{cvletter}

%%% Make a closing for Cover Letter using letter data
\makeletterclosing

\end{document}
